Accelerating adaptive ultrasound algorithms using graphics processing units \vspace{0.5cm}

### 2014-01-25 ThesisJP/Introduction/introduction.tex
Finished the discussion. Next background and revisions...

Objections to \textbf{Paper IV} includes its inherent chicken-or-egg dilemma. The visualization is adjusted based on the data acquired by a user. The user sees the visualization and adjust scanning based on the visual input. This recursive behavior suggest that the method is best suited for post-processing when data has been recorded and saved.

It is also clear that if the tracking fails the suggested method will fail.

Does data need to be saved in order to perform tracking?

View-dependent visibility.

Propose an method for automatic tuning of rendering parameters. Might be to extreme... A global opacity function based on global statistics combined with improved smothing, might be the future....

Statistics derived from the selected window by e.g Capon beamforming or the LCA beamformer might be utilized to adjust the opacity. It can also be used as input to image filtering. A adaptive window will be symmetric in homogeneous regions and left-right shifted close to tissue interfaces. In that way we can apply less filtering and higher opacity on edges. If this will be different than just looking at neighboring pixels is to be seen.

Integrated beamforming and visualization. Using adaptive beamforming to improve e.g. speckle tracking and segmentation. Use adaptive weight statistics to guide image smoothing.
\\\\
The fifth paper stands out from the other papers by not dealing with an adaptive processing technique. It is still, however, centered around the topic of GPU implementation of algorithms for ultrasound imaging. Ultrasound simulations are typically used for research and to pre-calculate configurations of a given scan sequence. The continuously growth in computational power will, in the future, make it possible to evaluate a scan sequence on the fly, removing the need for

Achieving higher processing speed for an excising algorithm is not impressive as long as there is no novel analysis of the method modification    and the increase does not enables new ways of utilizing the increased speed.

The simulator has been download 200 times and have close to 1000 views on youtube.

Fast calculation of pressure fields can be used to automatically evaluate the pressure field of the current scan sequence. Hence, we can optimize weights etc. on the fly.
\\\\
The code for both the Capon beamformer and the ultrasound field simulator have been made open source and is available on github\footnote{github.com/jpaasen/hos and github.com/jpaasen/cos}. 
\endinput

>>>>

%Objections to \textbf{Paper IV} includes its inherent chicken-or-egg dilemma. The visualization is adjusted based on the data acquired by a user. The user sees the visualization and adjust scanning based on the visual input. This recursive behavior suggest that the method is best suited for post-processing when data has been recorded and saved. 
%Does data need to be saved in order to perform tracking?
One limitation of the algorithm described in \textbf{Paper IV} is its dependence on a successful tracking. If the tracking fails the proposed method will fail.  Another issue is the view-dependent visibility, where an object could become visible or disappear while rotating or if the local statistics change a lot during the cardiac cycle. This means that the rendering will be come non-intuitive to interact with and unrealistic to watch. However, the method could be used to clean up still images of standard views. The paper does also propose an interesting method for automatic tuning of rendering parameters. Figure 3d in \textbf{Paper IV} actually shows that an optimal threshold could be found based on global statistics as well. Even though the final visualization has more errors, with respect to endocardium visibility, the tuning of the opacity function is fully automatic. An automatically tuned opacity function based on global statistics combined with improved smoothing could be the future for cardiac ultrasound imaging. It would also be interesting to see if statistics derived based on the window selected by the Capon or the LCA beamformer could be utilized to adjust the opacity. It should also be possible to use this statistic as input to image filtering. An adaptively selected window will be symmetric in homogeneous regions and left-right shifted close to tissue interfaces. In that way we can apply less filtering and higher opacity on edges. If this will be different than just looking at neighboring pixels is to be seen.
The fifth paper stands out from the other papers by not dealing with an adaptive processing technique. It is still, however, centered around the topic of implementing algorithms for ultrasound imaging on GPUs. Ultrasound simulations are typically used for research and to sometimes pre-calculate configurations of a given scan sequence to achieve a certain pressure in a given area. The continuously growth in computational power will, in the future, make it possible to evaluate a scan sequence on the fly, removing the need for lookup tables. Estimation of the mechanical and thermal index could also be improved. Achieving higher processing speed for an excising algorithm by implementing it on a new architecture is not academically relevant in its own. It has to combined with either a good analysis of what special adjustments that had to be made to the algorithm in order for the increase to happen or a suggestion of how to utilize the speed gained. These are points we have tried to answer in both \textbf{Paper I}, \textbf{II},  \textbf{III}, and \textbf{V}.  As a curiosity I would like to mention the as of January 2014 the simulator has been download 200 times and counting. It also has a "whopping" 1000 views on youtube. 
Finally it is worth mentioning that the code for both the Capon beamformer\footnote{github.com/jpaasen/cos} and the ultrasound field simulator\footnote{github.com/jpaasen/hos} have been made open source and is available on github. 
\endinput
